Democracy, Public Support, and Measurement Uncertainty

### 2021-04-29 paper/dcpo_demsupport.Rmd
original analysis in nice table

```{r claassenAPSR}
df_result_cls <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

@@

ls_mods[["ECM2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
    sd.plm,
    model = "pooling"
  )
ls_mods[["FD2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
    + plm::lag(Corrup_TI_z, 1),
    sd.plm,
    model = "pooling"
  )

@@

ls_mods[["ECM2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )
ls_mods[["FD2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod, conf.int = TRUE) %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

```{r cls2020a, results='asis', eval = TRUE}
ls_result_cls <-
  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
    ls_sum <- list(tidy = aTidy,
                   glance = aGlance)

@@

>>>>

```{r claassenAPSR, eval = TRUE}

@@

ls_mods[["ECM2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
    sd.plm,
    model = "pooling"
  )
ls_mods[["ECM2.2"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
    + plm::lag(Corrup_TI_z, 1),
    sd.plm,
    model = "pooling"
  )

@@

ls_mods[["FD2.1"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )
ls_mods[["FD2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

df_result_clsAPSR <- map(ls_mods, function(aMod){
  tidy(aMod, conf.int = TRUE) %>%
    mutate(std.error = vcovHC_se(aMod))
})

@@

```{r num-cls2020a, results='asis', eval = TRUE}
ls_result_cls <-
  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
    ls_sum <- list(tidy = aTidy,
                   glance = aGlance)

@@

```{r num-cls2020b, results='asis', eval = TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(ls_mods, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```
